% !TEX root = ../../main.tex
% !TEX spellcheck = en_GB

\section{Test}
\label{sec:test}
\subsection{Frequency determination}
\Cref{tab:test} shows the output of the Matlab model and the Blackfin implementation when determining the frequency of a \num{512} samples long input signal.
The Matlab model was run four times with four different inputs and applied a Hamming window, which the Blackfin implementation did not.
As can be seen the Matlab model is very precise in determining the frequency whereas the Blackfin implementation is slightly of.
The Blackfin being not as precise as the Matlab model can be attributed mostly to the lacking window and to quantization errors.

\begin{table}
	\centering
	\begin{tabular}{c | c c c c c | c}
		\toprule
		Test freq (Hz) & \multicolumn{4}{l}{Matlab freq (Hz)} & & Blackfin freq (Hz) \\
		\midrule
		\num{245} & \num{245.13} & \num{244.93} & \num{244.85} & \num{245.03} && \num{237}\\
		\num{350} & \num{349.90} & \num{349.94} & \num{349.88} & \num{349.96} && \num{349}\\
		\num{470} & \num{470.00} & \num{470.00} & \num{470.00} & \num{470.00} && \num{470} \\
		\num{521} & \num{521.22} & \num{521.18} & \num{521.10} & \num{521.04} && \num{525} \\
		\bottomrule
	\end{tabular}
	\caption{Tested frequencies and the found results using blocks of length \num{512}. Matlab results are the average of 4 blocks of \num{512} on a signal of length \num{2048}, each block windowed with a hamming window. It has been investigated if the \SI{470}{\hertz} results are due to an error, but it does not seem so.}
	\label{tab:test}
\end{table}

\subsection{Clock cycle usage}
A question to be asked is, "Can the processing of the signal occur before the next set of 512 samples?".
To find the answer for this, the clock cycles used of the FFT an the hilbert transform has been measured, and the amount of time at disposal has been calculated.

Time between sample blocks:
$td = \frac{samples}{fs} = \frac{512}{\SI{48}{\kilo\hertz}} = \SI{10.7}{\milli\second}$

Measurement of the clock cycles usage:
$\frac{1898733 cycles}{512 samples} = 3708 \frac{cyles}{sample}$.
Which is less then specified in the requirements.

The Blackfin has a maximum speed at \SI{600}{\mega\hertz}.
Which means it will take $\frac{\num{1898733}}{\SI{600}{\mega\hertz}} = {\SI{3.16}{\milli\second}}$ so the Hilbert transformation uses less time than the time it takes to sample 512 samples since $\SI{3.16}{\milli\second} < \SI{10.7}{\milli\second}$ and it uses less cycles pr. sample then specified in the requirements.
Concluding the Hilbert transform takes less time than it has at its disposal.

To generate 183 samples, with the sine generator it takes: $\frac{\num{26225} cycles}{183 samples} = \num{143.3}\frac{cycles}{sample}$.
This brings the total time of finding the frequency and generating one period of it up to \SI{3.21}{\milli\second}, still way below the threshold of \SI{10.7}{\milli\second}.

\subsubsection{Optimized clock cycle usage}
In the cross core environment it is possible to optimize the code with regards to size or speed.
This was done with three different settings for the optimization. 
Firstly where the size was the main focus of the optimization. 
Secondly the size and speed had same prioritization in the optimization settings.
And lastly where the speed was the focus. The result can be seen on
\begin{table}
	\centering
	\begin{tabularx}{0.95\textwidth}{l c c c c}
		\toprule
		{\textbf{Optimized for:}} & \textbf{None} & \textbf{Size} & \textbf{50\% Size 50\% Speed} & \textbf{Speed} \\
		\midrule
		\textbf{Hilbert transform} & \num{3708} & \num{3582} & \num{3577} & \num{3554} \\
		\textbf{Sine generator} & \num{143} & \num{115} & \num{115} & \num{115} \\
		\textbf{Total} & \num{3851} & \num{3697} & \num{3692} & \num{3669} \\
		\bottomrule
	\end{tabularx}
	\caption{The cycle usage with different settings for the optimization function in the cross core environment. Every value is shown in $\frac{\text{cycles}}{\text{sample}}$.}
	\label{OptimizedCycleUsage}
\end{table}

So if the code is optimized with regards to speed, the amount of cycles used becomes less, but a neglect able amount.  

\FloatBarrier